### 2014-03-15 src/analysis.Rnw
Adding the x\% selection for operators

>>>>

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xop), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xop), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The x\% per operator criteria results.}
\label{tbl:onesel}
\end{table*}

### 2014-03-15 src/paper.Rnw
Fix up table columns
switch delta
.
Adding the x\% selection for operators

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  return(x)
}

@@

>>>>

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  names(x)[names(x) == 'sampling'] <- '$\\div$'
  return(x)
}

@@

stats.xop <- subset(stats.rest, grepl('^OP', operator))
stats.rest <- subset(stats.rest, !grepl('^OP', operator))

o.stats.sel.xop <- subset(o.f(stats.xop), select=sel.colnames)
r.stats.sel.xop <- subset(r.f(stats.xop), select=sel.colnames)
colnames(o.stats.sel.xop) <- new.colnames
colnames(r.stats.sel.xop) <- new.colnames

o.stats.sel.xop$scope  <- 'op'
o.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
r.stats.sel.xop$scope  <- 'op'
r.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))

o.stats.sel.xop$operator  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
r.stats.sel.xop$operator  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))
